Constructing hierarchies

### 2023-10-05 analysis.Rmd
update analysis

# representators <- c("error", "ts", "error.features", "ts.features", "forecast")
#
# ## in most cases, error is the best
# representator_summarise %>% rowwise() %>%
#   mutate(min = representators[which.min(c(error, ts, error.features, ts.features, forecast))]) %>%
#   pull(min) %>%
#   table()
#
# ## only in one case, error is the worst
# representator_summarise %>% rowwise() %>%
#   mutate(max = representators[which.max(c(error, ts, error.features, ts.features, forecast))]) %>%
#   pull(max) %>%
#   table()
# mcb(representator_summarise %>% select(representators))

@@

tmp <- store_all %>% filter(distance == "")
tmp$rank <- do.call(cbind, tmp$values) %>% apply(1, rank) %>%
  t() %>% colMeans()

## 1. all the averaged random hierarchies beat no hierarchy
## 2. deep and wide hierarchy wins
## 3. average of more hierarchies does not obtain better results.
##   Some really bad hierarchies destroy the results.
##.  Deeper hierarchies have the ability to mitigate the affect of bad series

@@

cluster_summarise
# cluster_summarise %>% select(-c(representator, distance)) %>%
#   mcb()

## 1. kmedoids unnested is really bad
## 2. hcluster with single linkage is bad
## 3. nested kmedoids performs really well, which forms a natural-like unbalanced hierarchy.
```

@@

distance_summarise

# distance_summarise <- store_all %>% filter(distance != "") %>%
#   nest(values = c(distance, values, rank)) %>%
#   mutate_at("values", purrr::map, function(x){
#     x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
#       t() %>% colMeans() %>% rank()
#     x %>% select(-values) %>%
#       pivot_wider(names_from = "distance", values_from = "rank")
#   }) %>%
#   unnest("values")
# distance_summarise %>% select(-c(representator, cluster)) %>%
#   mcb()
#
# distances <- c("euclidean", "dtw", "negcor", "cor", "uncorrelation")
# distance_summarise %>% rowwise() %>%
#   mutate(max = distances[which.max(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
#   pull(max) %>%
#   table()
# distance_summarise %>% rowwise() %>%
#   mutate(min = distances[which.min(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
#   pull(min) %>%
#   table()
```

@@

```{r, include=FALSE, echo=FALSE}
store_all <- NULL
for (batch in 0:8) {
  store_all <- readRDS(paste0("tourism/store_", batch, ".rds"))$output %>%
    output_pre() %>% mutate(batch = batch) %>%
    filter(rf_method == .env$rf_method, accuracy_method == .env$accuracy_method) %>%
    dplyr::select(-rf_method, -accuracy_method) %>%
    rbind(store_all)
}

@@

@@

# representators <- c("error", "ts", "error.features", "ts.features", "forecast")
#
# ## in most cases, error is the best
# representator_summarise %>% rowwise() %>%
#   mutate(min = representators[which.min(c(error, ts, error.features, ts.features, forecast))]) %>%
#   pull(min) %>%
#   table()
#
# ## only in one case, error is the worst
# representator_summarise %>% rowwise() %>%
#   mutate(max = representators[which.max(c(error, ts, error.features, ts.features, forecast))]) %>%
#   pull(max) %>%
#   table()
# mcb(representator_summarise %>% select(representators))

# no hierarchy is not good: 391 / 428
print(sprintf("rank of no clustering: %s", rank(store_all$rank)[1]))

@@

tmp <- store_all %>% filter(distance == "")
tmp$rank <- do.call(cbind, tmp$values) %>% apply(1, rank) %>%
  t() %>% colMeans()

## 1. all the averaged random hierarchies beat no hierarchy
## 2. deep and wide hierarchy wins
## 3. average of more hierarchies does not obtain better results.
##   Some really bad hierarchies destroy the results.
##.  Deeper hierarchies have the ability to mitigate the affect of bad series

>>>>

@@

@@

@@

@@

```{r, include=FALSE, echo=FALSE}
store_all <- NULL
for (batch in 0:11) {
  store_all <- readRDS(paste0("tourism/store_", batch, ".rds"))$output %>%
    output_pre() %>% mutate(batch = batch) %>%
    filter(rf_method == .env$rf_method, accuracy_method == .env$accuracy_method) %>%
    dplyr::select(-rf_method, -accuracy_method) %>%
    rbind(store_all)
}

@@

### representor rank

```{r}
# representator rank
representor_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(representator, values, rank)) %>%
  mutate(orig_values = values) %>%
  mutate_at("values", purrr::map, function(x){

@@

representor_summarise <- representor_summarise %>%
  rowwise() %>% mutate(best = which.best(values),
                       sigbest = is.bestsignificant(values),
                       worst = which.worst(values),
                       sigworst = is.worstsignificant(values))

representors <- c("ts", "error", "ts.features", "error.features", "forecast")
for (method in representors) {
  print(sprintf("In %s cases, %s is the best, where %s is significantly best. In %s cases, it is the worst, where %s is significantly worse than the best one.",
                NROW(representor_summarise %>% filter(best == method)),
                method,
                NROW(representor_summarise %>% filter(best == method, sigbest)),
                NROW(representor_summarise %>% filter(worst == method)),
                NROW(representor_summarise %>% filter(worst == method, sigworst))))
}
```

```{r}
print(sprintf("rank of no clustering: %s/512", rank(store_all$rank)[which(store_all$cluster == "")]))
print(sprintf("rank of natural hierarchy: %s/512", rank(store_all$rank)[which(store_all$cluster == "natural")]))

@@

tmp <- store_all %>% filter(distance == "")
tmp$rank <- do.call(cbind, tmp$values) %>% apply(1, rank) %>%
  t() %>% colMeans()
tmp %>% arrange(rank)
```
